---
title: "Introduction to R-package"
author: "SA23204190"
date: "2023-12-4"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to R-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

_SA23204190__ is a simple R package developed to be a final project for the 'Statistical Computing' course. Three functions are considered, namely, NR,gibbsR and gibbsC



## NR

description:Newton-Raphson method using R

Parameter meanings：

f:function of which we want to find a root

df: derivative of f

x0: initial guess

return: Numerical solution of the equation

Functions have tolerant parameters=1e-4 and Maximum Number Of Iterations=1e4

The source R code for _NR_ is as follows:

```{R}
NR <- function(f,df,x0){
  x< - x0
  iter <- 0
  
  
  while (abs(f(x)) > 1e-4 && iter < 1e4) {
    x <- x-f(x)/df(x)
    iter <- iter + 1 
  }
  
  if (iter == 1e4) {  
    stop("Did not converge")  
    
  } else {  
    return(x) 
  }  
  
}
```


## gibbsR

description:A Gibbs sampler using R

Parameter meanings：

N the number of samples

thin the number of between-sample random numbers


The source R code for _gibbsR_ is as follows:
```{r}
gibbsR <- function(N, thin) {
  mat <- matrix(nrow = N, ncol = 2)
  x <- y <- 0
  for (i in 1:N) {
    for (j in 1:thin) {
      x <- rgamma(1, 3, y * y + 4)
      y <- rnorm(1, 1 / (x + 1), 1 / sqrt(2 * (x + 1)))
    }
    mat[i, ] <- c(x, y)
  }
  mat
}
```

## gibbsC

description A Gibbs sampler using Rcpp

Parameter meanings:

N: the number of samples

thin: the number of between-sample random numbers

return a random sample of size N

